Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-02-28 Submission.Rmd
Tuesday meeting updates (mostly results)

>Hypothesis 1: Job characteristics differ in constancy regarding subjective worker perception as a demand or resource.

@@

The Occupational Information Network (O\*Net) contains a comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors of most occupations in the US and these descriptions are continually updated. We retained 98 work [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work context statements were grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).

O\*Net collects information about these categories by periodically asking workers about these statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).  For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*. We retained O\*Net’s response scales, all of which shared the same 5-point scale regardless of semantic label difference. Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems (statements/questions).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

H1 proposes that job characteristics differ in constancy regarding subjective worker perception as a demand or resource. We explore this hypothesis first by item, and then present a more holistic picture. First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability. Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations. Note that the presentation is limited to 8 characteristics per perceived category only because of limited space. All sortable ratings are available in the online resources.

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand. A large proportion of correlations are moderate. Challenge and hindrance demands are smaller in relationship, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

In addition to the two hypotheses, three related research questions were proposed. To answer these research questions, authors first categorized items into the categories listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”. Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be "hindrances" at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. In sum, these results provide some support for RQ 1 and 2.

@@

NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.

>>>>

>Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.

@@

The Occupational Information Network (O\*Net) contains a comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated. We retained 98 work [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work *context* statements are grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).

O\*Net collects information about these categories by periodically asking workers job characteristic statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).  For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*. We retained O\*Net’s response scales, all of which shared the same 5-point scale regardless of semantic label difference. Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems (statements/questions).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the online survey. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*). Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.

@@

H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource. We explore this hypothesis first by item, and then present a more holistic picture. First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability. Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations. Note that the presentation is limited to 8 characteristics per perceived category only because of limited space. All sortable ratings are available in the online resources.

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand. A large proportion of correlations are moderate. Challenge and hindrance demands are smaller in relationship, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is percieved as a *resource* being also percieved as a *challenge*. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

In addition to the two hypotheses, two related research questions were proposed. To answer these research questions, authors first categorized items into the JD-R elements listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”. This O\*Net item was therefore retained within the "autonomy" category. Means for resource, challenge, and hindrance groupings were then computed to explore whether literature-implicated resources and demands were evaluated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. In sum, these results provide some support for RQ 1 and 2.

@@

### 2023-02-28 Submission.tex
Tuesday meeting updates (mostly results)

\begin{quote}
Hypothesis 1: Job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
\end{quote}

@@

The Occupational Information Network (O*Net) contains a comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors of most occupations in the US and these descriptions are continually updated. We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications} which O*Net groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work context statements were grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).

O*Net collects information about these categories by periodically asking workers about these statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. We retained O*Net's response scales, all of which shared the same 5-point scale regardless of semantic label difference. Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

H1 proposes that job characteristics differ in constancy regarding subjective worker perception as a demand or resource. We explore this hypothesis first by item, and then present a more holistic picture. First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability. Figure \ref{fig:combinegraphs} presents the top 8 resources, challenges, and hindrances characteristics that are \emph{largely agreed on} as indexed by (relatively) low standard deviations. Note that the presentation is limited to 8 characteristics per perceived category only because of limited space. All sortable ratings are available in the online resources.

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand. A large proportion of correlations are moderate. Challenge and hindrance demands are smaller in relationship, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

In addition to the two hypotheses, three related research questions were proposed. To answer these research questions, authors first categorized items into the categories listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''. Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. In sum, these results provide some support for RQ 1 and 2.

>>>>

\begin{quote}
Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
\end{quote}

@@

The Occupational Information Network (O*Net) contains a comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated. We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work \emph{context} statements are grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).

O*Net collects information about these categories by periodically asking workers job characteristic statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. We retained O*Net's response scales, all of which shared the same 5-point scale regardless of semantic label difference. Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the online survey. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}). Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.

@@

H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource. We explore this hypothesis first by item, and then present a more holistic picture. First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability. Figure \ref{fig:combinegraphs} presents the top 8 resources, challenges, and hindrances characteristics that are \emph{largely agreed on} as indexed by (relatively) low standard deviations. Note that the presentation is limited to 8 characteristics per perceived category only because of limited space. All sortable ratings are available in the online resources.

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand. A large proportion of correlations are moderate. Challenge and hindrance demands are smaller in relationship, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is percieved as a \emph{resource} being also percieved as a \emph{challenge}. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

In addition to the two hypotheses, two related research questions were proposed. To answer these research questions, authors first categorized items into the JD-R elements listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''. This O*Net item was therefore retained within the ``autonomy'' category. Means for resource, challenge, and hindrance groupings were then computed to explore whether literature-implicated resources and demands were evaluated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. In sum, these results provide some support for RQ 1 and 2.
